\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.45in]{geometry}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{enumitem}

\definecolor{primaryblue}{HTML}{0056b3}
\definecolor{darkgray}{HTML}{333333}

\hypersetup{
    colorlinks=true,
    linkcolor=primaryblue,
    urlcolor=primaryblue,
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\newcommand{\resumesection}[1]{%
  \vspace{6pt}%
  {\fontfamily{phv}\selectfont\textbf{\large\MakeUppercase{#1}}}%
  \vspace{2pt}%
  \hrule%
  \vspace{4pt}%
}

\setlist[itemize]{leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,label=\textbullet}

\begin{center}
    {\fontfamily{phv}\selectfont\textbf{\Huge AKHILESH KUMAR MISHRA}} \\
    \vspace{3pt}
    {\fontfamily{phv}\selectfont\large\textbf{\textcolor{primaryblue}{Software Development Engineer (MERN Stack)}}} \\
    \vspace{4pt}
    {\small
    \textcolor{primaryblue}{\faPhone*}~+91 88580 45785 \quad | \quad 
    \href{mailto:makhileshkumar1@gmail.com}{\textcolor{primaryblue}{\faEnvelope}~makhileshkumar1@gmail.com} \quad | \quad 
    \href{https://linkedin.com/in/akhilesh-kumar-mishra-a46030231}{\textcolor{primaryblue}{\faLinkedin}~linkedin.com/in/akhilesh-kumar-mishra} \quad | \quad 
    \href{https://github.com/GitHub-akhilesh}{\textcolor{primaryblue}{\faGithub}~github.com/GitHub-akhilesh}
    }
\end{center}
\vspace{-10pt}

\resumesection{Summary}
Software Development Engineer specializing in the MERN Stack, with a track record of building secure, high-scale FinTech and transaction tracking platforms. Expert in React.js, Next.js, Redux Toolkit, Node.js, Express.js, and MongoDB. Proven experience in optimizing database queries, building real-time dashboards via WebSockets, and migrating monoliths to high-performance Node microservices. Reduced transaction failure rates and biometric login latency by implementing robust authentication and asynchronous processing pipelines.

\resumesection{Experience}
{\textbf{Software Development Engineer}} \\
{\textbf{\textcolor{primaryblue}{CSC e-Governance Services India Ltd. (MeitY, Government of India)}}} \\
{\footnotesize\textcolor{primaryblue}{\faCalendar*}~12/2023 -- Present \quad | \quad \textcolor{primaryblue}{\faMapMarker*}~New Delhi, India}
\begin{itemize}
    \item Re-architected monolithic web portals into scalable \textbf{Node.js} and \textbf{Express.js} microservices, improving deployment speeds and fault isolation for 2 million+ active users.
    \item Built real-time location tracking and transaction monitoring dashboards using \textbf{React.js}, \textbf{Redux Toolkit}, and \textbf{WebSockets}, tracking 500,000+ daily transactions.
    \item Integrated third-party UPI and XML payment APIs using Node.js REST controllers, achieving 99\% transaction success rates for AEPS and MATM services under peak loads.
    \item Implemented secure authentication mechanisms using \textbf{Redis and JWT}, incorporating OTP expiry, rate limiting, and device binding.
    \item Tuned \textbf{MongoDB} database schemas using indexing, sharding, and Mongoose query optimizations, resulting in a 40\% reduction in database response times.
    \item Established automated CI/CD deployment pipelines using \textbf{Docker}, \textbf{Git}, and \textbf{GitHub Actions}, streamlining container deployments.
\end{itemize}

\vspace{4pt}
{\textbf{Freelance Software Engineer}} \\
{\textbf{\textcolor{primaryblue}{Workforce Telemetry \& Operations}}} \\
{\footnotesize\textcolor{primaryblue}{\faCalendar*}~06/2023 -- 11/2023 \quad | \quad \textcolor{primaryblue}{\faMapMarker*}~Remote, India}
\begin{itemize}
    \item Engineered and implemented a real-time workforce tracking application utilizing \textbf{React.js}, \textbf{Node.js}, \textbf{Express.js}, and \textbf{MongoDB}.
    \item Created an interactive map tracking interface using \textbf{React.js} and \textbf{Ant Design} (antd), incorporating real-time locations and alerts via WebSockets.
    \item Managed frontend state and query caching using \textbf{Redux Toolkit} and \textbf{React Query}, reducing redundant API calls by 45\%.
\end{itemize}

\resumesection{Projects}
{\textbf{MERN FinTech \& E-commerce Platform}} \\
{\small A collection of full-stack web applications featuring secure user authentication, interactive dashboards, and REST APIs built with React, Node, Express, and MongoDB.} \\
{\footnotesize\textbf{STACK:} React.js / Node.js / Express.js / MongoDB / JWT / Redux}

\vspace{4pt}
{\textbf{Himalayan Edges Website Development}} \\
{\small Created and launched an e-commerce platform using the MERN stack with PWA features, hosted on AWS, increasing page load speeds and client usage by 30\%.} \\
{\footnotesize\textbf{STACK:} React.js / Node.js / Express.js / MongoDB / PWA / AWS S3}

\vspace{4pt}
{\textbf{Facial Recognition Attendance Dashboard}} \\
{\small Created an automated student attendance tracking system integrating a Python face recognition script (OpenCV and LBPH) with a Node.js/Express backend API and a React dashboard.} \\
{\footnotesize\textbf{STACK:} React.js / Node.js / Express.js / Python / OpenCV / MySQL}

\vspace{4pt}
{\textbf{Traveling Portal \& Landing Page}} \\
{\small A fully responsive, modern front-end landing page for a travel agency built with HTML, CSS, and Bootstrap layouts.} \\
{\footnotesize\textbf{STACK:} HTML5 / CSS3 / JavaScript / Bootstrap}

\resumesection{Skills}
\textbf{Frontend:} React.js, Next.js, Redux Toolkit, JavaScript (ES6+), TypeScript, HTML5, CSS3, Tailwind CSS, Material UI, Bootstrap \\
\textbf{Backend \& APIs:} Node.js, Express.js, RESTful APIs, JWT Authentication, RBAC, WebSockets \\
\textbf{Data \& Messaging:} MongoDB, Mongoose, Redis cache, database schema design, indexing \\
\textbf{Tools \& Cloud:} Git, GitHub, Docker, Postman, CI/CD pipelines, GitHub Actions, AWS S3

\resumesection{Education}
{\textbf{B.Tech.}} \\
{\textbf{\textcolor{primaryblue}{Kanpur Institute of Technology}}} \\
{\footnotesize\textcolor{primaryblue}{\faCalendar*}~07/2019 -- 05/2023 \quad | \quad \textcolor{primaryblue}{\faMapMarker*}~Kanpur, UP}

\resumesection{Certifications}
Advanced MERN Stack Developer Certification \quad | \quad Database Systems & SQL Certification \\
Data Structures & Algorithms Certification \quad | \quad IIT Kanpur Cyber Security Certification

\resumesection{Achievements}
\begin{itemize}
    \item Graduated with First Class Honors, maintaining top academic rank.
    \item Earned a 4-Star Gold Badge in SQL on HackerRank.
\end{itemize}

\end{document}