\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.45in]{geometry}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{enumitem}

\definecolor{primaryblue}{HTML}{0c4f6b}
\definecolor{darkgray}{HTML}{333333}

\hypersetup{
    colorlinks=true,
    linkcolor=primaryblue,
    urlcolor=primaryblue,
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\newcommand{\resumesection}[1]{%
  \vspace{6pt}%
  {\fontfamily{phv}\selectfont\textbf{\large\MakeUppercase{#1}}}%
  \vspace{2pt}%
  \hrule%
  \vspace{4pt}%
}

\setlist[itemize]{leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,label=\textbullet}

\begin{center}
    {\fontfamily{phv}\selectfont\textbf{\Huge AKHILESH KUMAR MISHRA}} \\
    \vspace{3pt}
    {\fontfamily{phv}\selectfont\large\textbf{\textcolor{primaryblue}{Python Full Stack Developer}}} \\
    \vspace{4pt}
    {\small
    \textcolor{primaryblue}{\faPhone*}~+91 88580 45785 \quad | \quad 
    \href{mailto:makhileshkumar1@gmail.com}{\textcolor{primaryblue}{\faEnvelope}~makhileshkumar1@gmail.com} \quad | \quad 
    \href{https://linkedin.com/in/akhilesh-kumar-mishra-a46030231}{\textcolor{primaryblue}{\faLinkedin}~linkedin.com/in/akhilesh-kumar-mishra} \quad | \quad 
    \href{https://github.com/GitHub-akhilesh}{\textcolor{primaryblue}{\faGithub}~github.com/GitHub-akhilesh}
    }
\end{center}
\vspace{-10pt}

\resumesection{Summary}
Software Development Engineer specializing in Python Full Stack development, with a track record of building secure, scalable backend architectures and web systems. Expert in Python, Django, Django REST Framework (DRF), FastAPI, Celery, and database design in PostgreSQL/MySQL. Proven experience in migrating monoliths to async microservices, designing event-driven pipelines using Celery/Redis, and building real-time dashboards via WebSockets. Optimizes database queries and scales backend infrastructures using Docker.

\resumesection{Experience}
{\textbf{Software Development Engineer}} \\
{\textbf{\textcolor{primaryblue}{CSC e-Governance Services India Ltd. (MeitY, Government of India)}}} \\
{\footnotesize\textcolor{primaryblue}{\faCalendar*}~12/2023 -- Present \quad | \quad \textcolor{primaryblue}{\faMapMarker*}~New Delhi, India}
\begin{itemize}
    \item Re-architected monolithic web services into scalable, asynchronous \textbf{FastAPI} and \textbf{Django} microservices, improving reliability for 20 lakh+ users.
    \item Designed and scaled transaction orchestration services for AEPS, MATM, and VATM platforms using Django REST Framework, handling 5 lakh+ daily transactions.
    \item Implemented secure API authentication using \textbf{JWT} and role-based access control (\textbf{RBAC}), including OTP verification.
    \item Developed an asynchronous task queuing pipeline using \textbf{Celery} and \textbf{Redis} to handle high-volume wallet ledger records.
    \item Tuned \textbf{PostgreSQL} and \textbf{MySQL} database schemas using indexing and query partitioning, lowering transaction query latency.
    \item Constructed real-time transaction tracking APIs utilizing \textbf{FastAPI WebSockets} to stream live status updates.
\end{itemize}

\vspace{4pt}
{\textbf{Freelance Software Engineer}} \\
{\textbf{\textcolor{primaryblue}{Workforce Telemetry \& Operations}}} \\
{\footnotesize\textcolor{primaryblue}{\faCalendar*}~06/2023 -- 11/2023 \quad | \quad \textcolor{primaryblue}{\faMapMarker*}~Remote, India}
\begin{itemize}
    \item Developed a real-time workforce telemetry and geofencing system utilizing \textbf{FastAPI}, \textbf{SQLAlchemy} (asyncio), and \textbf{React.js}.
    \item Built an interactive live telemetry dashboard in \textbf{React} using Ant Design (antd) to visualize coordinates, speed, and geofences.
    \item Implemented a high-performance, asynchronous ingestion API to capture GPS locations (\texttt{/api/v1/tracking/ingest}) using \textbf{FastAPI}.
\end{itemize}

\resumesection{Projects}
{\textbf{Facial Recognition Attendance Dashboard}} \\
{\small Developed an automated student attendance tracking application in Python using OpenCV (Haarcascade \& LBPH) and MySQL, with custom Excel reports via Pandas.} \\
{\footnotesize\textbf{STACK:} Python / OpenCV / Tkinter / MySQL / Pandas}

\vspace{4pt}
{\textbf{Himalayan Edges Website Development}} \\
{\small Created an e-commerce platform using Django and React.js with PWA features, hosted on AWS, boosting page speeds and usage by 30\%.} \\
{\footnotesize\textbf{STACK:} Python / Django / React.js / SQLite / AWS / PWA}

\vspace{4pt}
{\textbf{Persistent Task Management Dashboard}} \\
{\small Programmed a desktop utility for task planning, category filtering, and JSON data persistence, featuring clean MVC architecture patterns.} \\
{\footnotesize\textbf{STACK:} Python / Tkinter / JSON / MVC Patterns}

\vspace{4pt}
{\textbf{Traveling Portal \& Landing Page}} \\
{\small A fully responsive, modern front-end landing page for a travel agency designed with HTML, CSS, and Bootstrap layouts.} \\
{\footnotesize\textbf{STACK:} HTML5 / CSS3 / JavaScript / Bootstrap}

\resumesection{Skills}
\textbf{Backend:} Python, Django, FastAPI, Celery, Django REST Framework, SQLAlchemy (asyncio), Pandas \\
\textbf{Frontend \& APIs:} React.js, JavaScript, HTML5, CSS3, Bootstrap, RESTful APIs, WebSockets, JWT Security \\
\textbf{Data \& Messaging:} PostgreSQL, MySQL, SQLite, Redis cache/broker, database schema design, query indexing \\
\textbf{Tools \& Cloud:} Git, GitHub, Docker, Postman, Linux environments, OpenCV, LBPH face recognition

\resumesection{Education}
{\textbf{B.Tech.}} \\
{\textbf{\textcolor{primaryblue}{Kanpur Institute of Technology}}} \\
{\footnotesize\textcolor{primaryblue}{\faCalendar*}~07/2019 -- 05/2023 \quad | \quad \textcolor{primaryblue}{\faMapMarker*}~Kanpur, UP}

\resumesection{Certifications}
GeeksforGeeks MERN Stack Certification \quad | \quad Coding Ninjas DBMS Certification \\
Coding Ninjas DSA Certification \quad | \quad IIT Kanpur Prutor Cyber Security Certification

\resumesection{Achievements}
\begin{itemize}
    \item Graduated with First Class Honors, maintaining top academic rank.
    \item Earned a 4-Star Gold Badge in SQL on HackerRank.
\end{itemize}

\end{document}